---
Main code to analyze the Dow Jones Industrial Average
---
# General Setting

```{r}
# install.packages("ggplot2")
library(ggplot2)
```

# Data Preparation
## grab from Yahoo! Finance

1. install and import relative packages
```{r}
# install.packages("quantmod")
# install.packages("TTR")
library("TTR")
library("quantmod")
```

2. use 'getSymbols' to grab data
  Symbols: first parameter, specify the stock code
  src: specify the source
  from/to: specify the required period
  auto.assign: *False* for return the result
```{r}
df.DJI <- getSymbols("^DJI",
                     src = "yahoo",
                     from = "2016-01-01",
                     to = "2022-12-31",
                     auto.assign = FALSE)
summary(df.DJI)
```
3. extract the closing prices and take logarithm. Then, get the increment
```{r}
x.n <- df.DJI$DJI.Close
y.n <- log(x.n)
z.n <- diff(y.n)
summary(z.n)
```

# Data Cleaning

1. install and import relative packages
```{r}
# install.packages("e1071")
library(e1071)
```

y.n: from y_0 to y_1762
z.n: z_1 = y_1 - y_0, and so on
```{r, fig.height=10, fig.width=10}
df.z.n <- as.data.frame(z.n)
df.z.n$time <- 1:nrow(z.n)
df.z.n <- df.z.n[-1,]
mean.z <- mean(df.z.n$DJI.Close)
var.z <- var(df.z.n$DJI.Close)
quartile1 <- quantile(df.z.n$DJI.Close)[2]
quartile2 <- quantile(df.z.n$DJI.Close)[3]
quartile3 <- quantile(df.z.n$DJI.Close)[4]
IQR <-  quartile3 - quartile1
ggplot(df.z.n, aes(x = time, y = DJI.Close)) +
  geom_line(data = subset(df.z.n, time < 999 | time > 1503), color ="grey60") +
  geom_line(data = subset(df.z.n, time >= 999 & time <= 1503), color ="grey20") +
  geom_abline(
    intercept = c(mean.z - 3 * IQR, mean.z - 1.5 * IQR, mean.z + 1.5 * IQR, mean.z + 3 * IQR),
    slope = 0,
    linetype = c("dashed", "dashed", "dashed", "dashed"),
    color = c("darkblue", "darkred", "darkred", "darkblue")
  )
```
remove outliers
```{r}
# remove outliers

# mean.cleanz <- mean()
# var.cleanz <- var()
# skew.cleanz <- skewness()
# kurt.cleanz <- kurtosis() -3
```

# Standard Test of Normality
## Kolmogorov-Smirnov test and Anderson-Darling test

```{r}

```

# Investigation of Normality by Resampling

```{r}

```

# Investigation of Constant Mean

```{r}

```

# Investigation of Constant Variance

```{r}

```

# Investigation of Independence

```{r}

```

# Real Returns

1. install and import relative packages
```{r}
# install.packages("rvest")
library(rvest)
```

2. data preparation
```{r}
url <- "https://www.rateinflation.com/consumer-price-index/usa-historical-cpi?start=1&end=100"
webpage <- read_html(url)
cpi.data <- webpage %>%
  html_table() %>%
  data.frame()
rownames(cpi.data) <- cpi.data$Year
cpi.data <- cpi.data[, -1]
select.cpi.data <- cpi.data[9:2,]
```

```{r}
# real.DJI <- 
y.t.n <- log(real.DJI)
z.t.n <- diff(y.t.n)
```

3. Tests and Confidence Intervals
```{r}

```

